---
title: "Analysis"
output: pdf_document
date: "2024-10-10"
---

```{r imports}
library(ggplot2)
```

## Including zero results

```{r data}
data1 <- read.csv('./hospital-3-closest.csv')

head(data)
```

```{r plot}
ggplot(data1, aes(x = shortest_path, y=n_cameras, color=majority)) +  geom_point() + geom_smooth(method = "lm", se = FALSE)
```

Predicting the distance based on demographics

```{r regression}
linmod1 <- lm(shortest_path ~ majority, data=data1)

summary(linmod1)
```

Predicting the number of cameras depending on the distance and demographics

```{r regression}
linmod <- lm(n_cameras ~ shortest_path + majority, data=data)

summary(linmod)
```

## Only including paths that have cameras

```{r data}
data <- na.omit(read.csv('./hospital-3-closest-nonzero.csv'))

head(data)
```

```{r plot}
ggplot(data, aes(x = shortest_path, y=n_cameras, color=majority)) +  geom_point() + geom_smooth(method = "lm", se = FALSE)
```

```{r plot}
ggplot(data, aes(x = shortest_path, y=shortest_restricted_path, color=majority)) +  geom_point() + geom_smooth(method = "lm", se = FALSE)
```

Predicting the distance based on demographics

```{r regression}
linmod <- lm(shortest_path ~ majority, data=data)

summary(linmod)
```
Predicting the added distance based on demographics
```{r regression}
linmod <- lm(shortest_restricted_path ~ shortest_path + majority, data=data)

summary(linmod)
```

Predicting the number of cameras depending on the distance and demographics

```{r regression}
linmod <- lm(n_cameras ~ shortest_path + majority + 0, data=data)

summary(linmod)
```